Starcode: sequence clustering based on all-pairs search

### 2015-01-19 doc/document.tex
Corrected typos in manuscript and README.md.

%% Synthetic data %%
The performance of sequence clustering algorithms can be sensitive
to the size of the clusters in the dataset, which in many applications
is not known \textit{a priori}. We therefore set up a benchmark on
artificial datasets to test the accuracy and the scaling of the
tools on a known cluster structure. We generated 4 datasets of 1 million
50-mers arranged in 1 to 1,000 clusters. Each cluster consisted
of 100 repeats of the same centroid sequence, plus satellites
derived from the centroid by incorporating 3 errors including at
most 1 indel. The number of satellites per cluster ranged from
999900 to 900. Rainbow was not tested on this benchmark because
the generated data are single reads. In addition, evaluating the
exactness of slidesort was problematic because the number of
3-matches in each dataset is not known (pairs of statellites
in the same cluster may be 3-matches or not). For this reason
we only compared the number of pairs found by starcode with
the number of pairs found by slidesort. The outcome of the test
is summarized in Figure \ref{fig:benchmark}.

@@

\begin{table}[h]
\centering
\caption{Running time (in seconds) of the software on three biological
datasets. Exact running time was not recordeed past 10 days.
A dash indicates that the software cannot be used for this dataset.}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{SRR950457} &
      \textit{PRJEB7686} & \textit{SRR950477} \\ \hline
    starcode   & 5           & 2,898       & 44    \\
    seed       & -           & 60,374      & -     \\
    sidesort   & 4,055       & $>$ 10 days & -     \\
    rainbow    & -           & -           & 306   \\
    cd-hit-est & 170         & 512,591     & -     \\
\end{tabular}
\label{tab:biobench_runtime}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Memory usage (in GB).}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{SRR950457} &
      \textit{PRJEB7686} & \textit{SRR950477} \\ \hline
    starcode   & 0.65 & 30.9 & 5.2 \\
    seed       & -    & 53.9 & -   \\
    sidesort   & 1.30 & 13.9 & -   \\
    rainbow    & -    & -    & 0.5 \\
    cd-hit-est & 0.80 & 28.5 & -   \\
\end{tabular}
\label{tab:biobench_memory}
\end{table}

>>>>

%% Synthetic data %%
The performance of sequence clustering algorithms can be sensitive
to the size of the clusters in the dataset, which in many applications
is not known \textit{a priori}. We therefore set up a benchmark on
artificial datasets to test the accuracy and the scaling of the
tools on a known cluster structure. We generated 4 datasets of 1 million
50-mers arranged in 1 to 1,000 clusters. Each cluster consisted
of 100 repeats of the same centroid sequence, plus satellites
derived from the centroid by incorporating 3 errors including at
most 1 indel. The number of satellites per cluster ranged from
999900 to 900. Rainbow was not tested on this benchmark because
the generated data are single reads. In addition, evaluating the
exactness of slidesort was problematic because the number of
3-matches in each dataset is not known (pairs of satellites
in the same cluster may be 3-matches or not). For this reason
we only compared the number of pairs found by starcode with
the number of pairs found by slidesort. The outcome of the test
is summarized in Figure \ref{fig:benchmark}.

@@

\begin{table}[h]
\centering
\caption{Running time (in seconds) of the software on three biological
datasets. Exact running time was not recordeed past 10 days.
A dash indicates that the software cannot be used for this dataset.}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{SRR950457} &
      \textit{PRJEB7686} & \textit{SRR950477} \\ \hline
    starcode   & 5           & 2,898       & 44    \\
    seed       & -           & 60,374      & -     \\
    slidesort   & 4,055       & $>$ 10 days & -     \\
    rainbow    & -           & -           & 306   \\
    cd-hit-est & 170         & 512,591     & -     \\
\end{tabular}
\label{tab:biobench_runtime}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Memory usage (in GB).}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{SRR950457} &
      \textit{PRJEB7686} & \textit{SRR950477} \\ \hline
    starcode   & 0.65 & 30.9 & 5.2 \\
    seed       & -    & 53.9 & -   \\
    slidesort   & 1.30 & 13.9 & -   \\
    rainbow    & -    & -    & 0.5 \\
    cd-hit-est & 0.80 & 28.5 & -   \\
\end{tabular}
\label{tab:biobench_memory}
\end{table}
